### 2024-07-26 conteudo/introduction/intro.tex
add design diagram
adjust research figure and intro tex

@@

(POINTS TO CONSIDER: I do not like much this introduction, but is the best I could do)
(I DO NOT HAVE MORE A PLACE TO FIT THIS PARAGRAPH) An additional usefulness of our proposed approach, which we do not verify
in our research, is to give a new method to people become 
contributors to the Linux kernel. The process of starting to contribute to the Linux kernel can be unintuitive, which can cause 
people to distance themselves. Our approach provides to the community a new form of newcomers to start contributing by removing 
simple code duplications, while they learn the whole process of being a Linux contributor.

Figure (CREATE FIGURE AND ADD HERE) sumamarizes the research steps proposed in this work.

>>>>

\begin{figure}
\includegraphics[scale=0.7]{research_design}
\caption{Diagram of the research design.}
\label{fig:reDesign}
\end{figure}

@@

Figure \ref{fig:reDesign} sumamarizes the research steps proposed in this work.
